### 2018-03-21 Paper/jaccardbaetica.tex
update intro

%Roman trade has been an object of study in the last centuries. 
%hablar de que diferentes modelos se han utilizado como el de brumel, el ikasen de las redes, xavi pero qeu lo vamos a probar a microescala para ver si rula o no.

@@

% Debate
In archaeology, this debate has been widely studied in the last centuries (CITAR). Specifically, our work pretend to identify production processes focus on the olive oil trade.

@@

%Hyphotesis
However, some challenges remain under discussion such as how this province was organized and whether it is possible to identify production patterns in the olive oil trade (AMPLIAR Y METER SELLOS). Neither written evidences have been found that it could explain the economic role of Baetica province in the Roman organization. On the other hand, archaeological evidence show a highly specialized production with a long activity in a this specific area with apparently few changes \citep{remesal_anforas_2004}.

@@

Aquí poner algo sobre esto

>>>>

%Roman trade has been an object of study in the last centuries.

@@

% Debate
The discussion about the production processes in Baetican area due to the lack of written sources
In archaeology, this debate has been widely studied in the last centuries (CITAR). Despite this knowledge the application of new methodology to understand the Roman trade has allowed us to deal with the complexity of Roman Market combined with archaeological evidence \citep{orengo_seeds_2016,brughmans_roman_2016,coto-sarmiento_maria_bayesian_????}. Specifically, our work pretend to detect economic processes in a microescala focused in a commercial product from a specific province \citep{isaksen_network_2006}.

@@

%Hyphotesis
However, some challenges remain under discussion such as how this province was organized and whether it is possible to distinguish production patterns in the olive oil trade. Our questions will be focused on the distribution of amphoric stamps. Did they follow some distribution pattern? Did stamps share the same workshop? Neither written evidences have been found that it could explain the economic role of Baetica province in the Roman organization. On the other hand, archaeological evidence show a highly specialized production with a long activity in a this specific area with apparently few changes \citep{remesal_anforas_2004}.

@@
